\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
pass on section 3

\author{M. M. Abid Naziri}
\affiliation{%
  \institution{NC State University}
  %\city{Rocquencourt}
  \country{USA}
}
\email{mnaziri@ncsu.edu}

\author{Aman Kumar Singh}
\affiliation{%
 \institution{Amrita Vishwa Vidyapeetham}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{India}}
\email{amanks@am.amrita.edu}

\author{Feiran Qin}
\affiliation{%
 \institution{NC State University}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{USA}}
\email{fqin2@ncsu.edu}

\author{Benjamin Wu}
\affiliation{%
 \institution{Purdue University}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{USA}}
\email{wu2059@purdue.edu}

\author{Saikat Dutta}
\affiliation{%
 \institution{Cornell University}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{USA}}
\email{saikatd@cornell.edu}

\author{Marcelo d'Amorim}
\affiliation{%
 \institution{NC State University}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{USA}}
\email{mdamori@ncsu.edu}

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build, and column ``environment'' shows the breakdown
of instances for each kind of environment to reproduce the bug. Co-incidentally,
all bugs that require a GPU build are reproduced using a docker
container i.e. the column venv-docker is the same as bugs reproducible with CPU-GPU builds
of the libraries respectively. Table~\ref{table:bug-stats} shows whay type of error is manifested
due to each bug instance. In total, we have \numbugtypes\ different types of bug manifestations across
the three libraries.

\Fix{Added table and description, please revise}

@@

\textbf{Bugs.}~We focus on issue reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the issue reports have the label "bug" and have been fixed with pull
requests linked to them. We then create a filter that incorporates
the periods mentioned above, the label, the issue status being closed
and the presence of a linked pull request. We found \numtorchfiltered{}
issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
issues for \jax after filtering the issues. \torch has the highest number
of issues due to a lack of a label for bugs in the issue tracker.

We then manually inspect the
filtered issues to ensure that they contain enough information to
reproduce the bug, i.e.,
code to reproduce the bug, dependencies required for the bug
reproduction, clear description of the desired behavior,
etc. We also filter bugs that are not in the core functionality
of the library e.g. documentation issues, feature requests, etc.
After this stage of manual inspection, we end up with \numtorchinspected{}
issues for \torch, \numtfinspected{} issues for \tf, and \numjaxinspected{}
issues for \jax.

% Among these confirmed bug reports, we choose
% the ones that have enough information to reproduce the bugs, i.e.,
% code to reproduce the bug, dependencies required for the bug
% reproduction
% \Fix{Abid, can you confirm that environment here is not
%   the same as venv-docker that we are using on Table 1? instead it
%   means the version of CUDA, libraries, etc.? If so, avoid (re)using the
%   word environment.}
% , clear description of the desired behavior,
% etc. 
Afterwards, we assess the reproducibility of the bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug.
Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset. Through this process, we end up with \numtorchbugs{},
\numtfbugs{}, and \numjaxbugs{} bug instances for \torch, \tf,
and \jax, respectively.

\Fix{Abid: Added what labels were used, which period we took the issues from,
how many issues we looked at, defined "bug reports", mentioned how many bugs had 
been filtered with each criterion. Please review and revise}

\begin{table}
  \centering
  \caption{\label{table:bug-stats}Different bug manifestation types from \tname.}
  \begin{tabular}{lrrrr}\toprule
    Bug manifestation type &Jax &Pytorch &Tensorflow \\\midrule
    Incorrect Output &14 &11 &5 \\
    Internal Exception &11 &9 &4 \\
    Value Error &7 &0 &4 \\
    Type Error &3 &2 &3 \\
    Attribute Error &2 &0 &2 \\
    Index Error &2 &1 &0 \\
    Floating Point Error &1 &0 &0 \\
    Error Not Raised &1 &0 &0 \\
    Parse Error &1 &0 &0 \\
    Runtime Warning &1 &0 &0 \\
    Not Implemented Error &1 &0 &0 \\
    Memory Error &1 &1 &0 \\
    Invalid Argument Error &1 &0 &1 \\
    Runtime Error &0 &7 &1 \\
    Assertion Error &0 &2 &0 \\
    Segmentation Fault &0 &2 &1 \\
    Floating Point Exception &0 &1 &0 \\
    Aborted &0 &1 &8 \\
    \midrule
    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\textbf{Handling bugs in specific GPU-CUDA versions requires OS
  changes:} Some GPU-related bug instances can only be reproduced with
specific versions of CUDA~\cite{cuda}, NVIDIA's platform and API for
programming GPUs. These instances require specific CUDA drivers to be
installed on the system. Python virtual enviroments are not designed
to enable change of OS drivers.
% GPU builds\Fix{I don't understance GPU builds. do you mean
%   GPU vendor/version? give example} and specific CUDA builds. 
% Changing different virtual environments does not change the CUDA
% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
%   GPU) version with Python's virtual environments''?} of the
% system. 
% That is why we use Docker when a bug relies on a specific
% version of CUDA to be installed in the system.
We use Docker containers~\cite{merkel2014docker} for the bug instances
that require changes in drivers.

@@

\textbf{Example}
% ~\Fix{Can you show here the artifacts associated to bug
%   120903 that you will use in the next section? If it takes too much
%   space, show only directory with files and the test case. - Abid: by the test case, do you mean the python code used to reproduce the bug?} 
  The issue no. 120903 in pytorch has the following test code that checks the oracle:

>>>>

\author{M. M. Abid Naziri}
\affiliation{%
  \institution{NC State University, USA}
  %\city{Rocquencourt}
  \country{}
}
\email{mnaziri@ncsu.edu}

\author{Aman Kumar Singh}
\affiliation{%
 \institution{Amrita Vishwa Vidyapeetham, India}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{amanks@am.amrita.edu}

\author{Feiran Qin}
\affiliation{%
 \institution{NC State University, USA}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{fqin2@ncsu.edu}

\author{Benjamin Wu}
\affiliation{%
 \institution{Purdue University, USA}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{wu2059@purdue.edu}

\author{Saikat Dutta}
\affiliation{%
 \institution{Cornell University, USA}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{saikatd@cornell.edu}

\author{Marcelo d'Amorim}
\affiliation{%
 \institution{NC State University, USA}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{mdamori@ncsu.edu}

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build (release or nightly), and column
``environment'' shows the breakdown of instances for each kind of
environment to reproduce the bug (venv or docker). Co-incidentally,
all bugs that require a GPU build are reproduced using a docker
container, i.e. the column venv-docker matches would have been
observed with a column CPU-GPU, to indicate if the bug is can be
reproduced with a CPU or if it requires a
GPU. Table~\ref{table:bug-stats} shows the breakdown error types for
the bugs in our dataset. The row ``Incorrect Output'' is listed first
as it requires a distinct kind of oracle comparing consistency of the
outputs of test runs on a CPU and on GPU. In total, we have
\numbugtypes\ different types of bug manifestations across the three
libraries.

@@

\textbf{Bugs.}~We focus on issue reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the issue reports have the label "bug" and have been fixed with pull
requests linked to them. We then create a filter that incorporates
the periods mentioned above, the label, the issue status being closed
and the presence of a linked pull request. We found \numtorchfiltered{}
issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
issues for \jax after filtering the issues. \torch has the highest number
of issues due to a lack of a label for bugs in the issue tracker.
%%
Then, we manually inspect the filtered issues to ensure that they
contain enough information to reproduce the bug, i.e., code to
reproduce the bug, dependencies required for the bug reproduction,
clear description of the desired behavior, etc. We discard bugs that
are not in the core functionality of the library e.g. documentation
issues, feature requests, etc. After this stage of manual inspection,
we end up with \numtorchinspected{} issues for \torch,
\numtfinspected{} issues for \tf, and \numjaxinspected{} issues for
\jax.
%
Finally, we assess the reproducibility of the bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug.  Once we can successfully reproduce the bug by
creating the enviroment detailed in the report, we include the
corresponding artifacts in our dataset. Throughout this process, we
obtain \textbf{\numjaxbugs{}}, \textbf{\numtorchbugs{}}, and
\textbf{\numtfbugs{}} bug instances for \jax, \torch, and \tf,
respectively.

% Among these confirmed bug reports, we choose
% the ones that have enough information to reproduce the bugs, i.e.,
% code to reproduce the bug, dependencies required for the bug
% reproduction
% \Fix{Abid, can you confirm that environment here is not
%   the same as venv-docker that we are using on Table 1? instead it
%   means the version of CUDA, libraries, etc.? If so, avoid (re)using the
%   word environment.}
% , clear description of the desired behavior,
% etc.

%% \Fix{Abid: Added what labels were used, which period we took the issues from,
%% how many issues we looked at, defined "bug reports", mentioned how many bugs had 
%% been filtered with each criterion. Please review and revise}

\begin{table}
  \centering
  \caption{\label{table:bug-stats}Different bug manifestation types
    from \tname.\Fix{If time allows, add a total column and sort rows
      according to it (except incorrect output)}}
  \begin{tabular}{lrrrr}\toprule
    Bug manifestation type &Jax &Pytorch &Tensorflow \\\midrule
    Incorrect Output &14 &11 &5 \\
    Internal Exception &11 &9 &4 \\
    Value Error &7 &0 &4 \\
    Type Error &3 &2 &3 \\
    Attribute Error &2 &0 &2 \\
    Index Error &2 &1 &0 \\
    Floating Point Error &1 &0 &0 \\
    Error Not Raised &1 &0 &0 \\
    Parse Error &1 &0 &0 \\
    Runtime Warning &1 &0 &0 \\
    Not Implemented Error &1 &0 &0 \\
    Memory Error &1 &1 &0 \\
    Invalid Argument Error &1 &0 &1 \\
    Runtime Error &0 &7 &1 \\
    Assertion Error &0 &2 &0 \\
    Segmentation Fault &0 &2 &1 \\
    Floating Point Exception &0 &1 &0 \\
    Aborted &0 &1 &8 \\
    \midrule
    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\vspace{0.5ex}\noindent\textbf{Handling bugs in specific GPU-CUDA
  versions requires OS changes:} Some GPU-related bug instances can
only be reproduced with specific versions of CUDA~\cite{cuda},
NVIDIA's platform and API for programming GPUs. These instances
require specific CUDA drivers to be installed on the system. Python
virtual enviroments are not designed to enable change of OS drivers.
% GPU builds\Fix{I don't understance GPU builds. do you mean
%   GPU vendor/version? give example} and specific CUDA builds. 
% Changing different virtual environments does not change the CUDA
% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
%   GPU) version with Python's virtual environments''?} of the
% system. 
% That is why we use Docker when a bug relies on a specific
% version of CUDA to be installed in the system.
We use Docker containers~\cite{merkel2014docker} for the bug instances
that require changes in drivers.

@@

\textbf{Example}
% ~\Fix{Can you show here the artifacts associated to bug
%   120903 that you will use in the next section? If it takes too much
%   space, show only directory with files and the test case. - Abid: by the test case, do you mean the python code used to reproduce the bug?} 
  The issue no. 120903 in \torch\ has the following test code that checks the oracle:
